DATA 621 - Business Analytics and Data Mining

### 2020-11-08 HW4/HW4_Draft.Rmd
Unordered list slight cleanup

* `AGE`  
  + Since the data set is comprised of auto insurance policyholder information,
  the missing `AGE` values required imputation. However, given the relatively
  small number of missing values, imputation by predictive mean matching is
  conducted.

* `HOME_VAL`  
  + A `HOME_VAL` response of '0' makes it understandable to assume that those
  missing entries could indicate that the policyholder is a renter rather than a
  homeowner. Therefore, missing values were replaced with zeroes. The new `OWN`
  variables created in Model Set #1 is kept in Model Set #2.

* `CAR_AGE`, `INCOME` & `YOJ`  
  + Because there is a larger number of missing values (NA’s) were identified, 
  imputation by predictive mean matching is conducted.

  + Moreover, there is a single negative value ('-3') for `CAR_AGE` which seemed 
  implausible and was assumed to be a typographical error. Thus, the absolute
  value of `CAR_AGE` is taken.

@@

* `CAR_AGE.f`  
  + Because `CAR_AGE` is dominated by values of 1 (i.e. car being one year old
  or less), the `CAR_AGE.f` variable is derived as a factor variable to be used
  during the binary logistic regression modeling process. Therefore, it is
  interpreted as:

    `CAR_AGE.f` = 0: The vehicle is 1 year old or less.  
    `CAR_AGE.f` = 1: The vehicle is more than a 1-year-old.

* `HOMEKIDS.f` & `KIDSDRIV.f` 
   + Both the `HOMEKIDS` and `KIDSDRIV` variables indicated that large
   percentages of the values of each were 0. Therefore, both variables were
   converted to binary variables. The following is their binary interpretations:

      `HOMEKIDS.f` = 0: The policyholder has no child living at home.  
      `HOMEKIDS.f` = 1: The policyholder has 1 or more children living at home.  
      `KIDSDRIV.f` = 0: No teenage drivers use the policyholder’s insured
      vehicle.  
      `KIDSDRIV.f` = 1: One or more teenage drivers use the policyholder’s
      insured vehicle.

>>>>

  * `AGE`  
    * Since the data set is comprised of auto insurance policyholder information,
    the missing `AGE` values required imputation. However, given the relatively
    small number of missing values, imputation by predictive mean matching is
    conducted.
  * `HOME_VAL`  
    * A `HOME_VAL` response of '0' makes it understandable to assume that those
    missing entries could indicate that the policyholder is a renter rather than
    a homeowner. Therefore, missing values were replaced with zeroes. The new
    `OWN` variables created in Model Set #1 is kept in Model Set #2.
  * `CAR_AGE`, `INCOME` & `YOJ`
    * Because there is a larger number of missing values (NA’s) were identified,
    imputation by predictive mean matching is conducted.
    * Moreover, there is a single negative value ('-3') for `CAR_AGE` which
    seemed implausible and was assumed to be a typographical error. Thus, the
    absolute value of `CAR_AGE` is taken.

@@

* `CAR_AGE.f`  
  * Because `CAR_AGE` is dominated by values of 1 (i.e. car being one year old
  or less), the `CAR_AGE.f` variable is derived as a factor variable to be used
  during the binary logistic regression modeling process. Therefore, it is
  interpreted as:
    * `CAR_AGE.f` = 0: The vehicle is 1 year old or less.
    * `CAR_AGE.f` = 1: The vehicle is more than a 1-year-old.
* `HOMEKIDS.f` & `KIDSDRIV.f` 
   * Both the `HOMEKIDS` and `KIDSDRIV` variables indicated that large
   percentages of the values of each were 0. Therefore, both variables were
   converted to binary variables. The following is their binary interpretations:
     * `HOMEKIDS.f` = 0: The policyholder has no child living at home.
     * `HOMEKIDS.f` = 1: The policyholder has 1 or more children living at home.
     * `KIDSDRIV.f` = 0: No teenage drivers use the policyholder’s insured
      vehicle.
     * `KIDSDRIV.f` = 1: One or more teenage drivers use the policyholder’s
      insured vehicle.
